---
title: "Assignment2"
author: "Tharindu Madusanka Uyanahewa s4668998"
date: "1/3/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE) 
```

<!--install.packages("widyr")
install.packages("randomForest")
install.packages("data.table", dependencies=TRUE)
install.packages("plotly") -->

```{r}



library(data.table)
library(plotly)

library(randomForest)
library(yaml)
library(tidyverse)
library(knitr)
library(dplyr)
library(skimr)
library(tibble)
library(rmarkdown) 
library(tidyr)
library(ggplot2)
library(ggforce)

library(widyr)



```


```{r}

thanksgiving_meals <- read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-11-20/thanksgiving_meals.csv")



```

<!--``` {r}

thanksgiving_mealsV2 <- thanksgiving_meals

thanksgiving_mealsV2 
thanksgiving_mealsV2$family_income = as.factor(thanksgiving_mealsV2$family_income)

factor(thanksgiving_mealsV2$family_income)
str(thanksgiving_mealsV2)

class(thanksgiving_mealsV2$family_income)




``` -->


#1. Create an Rmarkdown document with webpage as output (same as in setup)

#At the start of the output document include your name in italic font and 
#your student id in bold font as level 2 heading


*Tharindu Uyanahewa*


## **s4668998**




#--------------------------------------------------------------------------------------------------------

### Part 2: Data Wrangling and visualization


#1. Display the first 10 rows of the dataset using `kable()` function

```{r}

head(thanksgiving_meals,10) %>%
  kable() 

```




#2. Using `skim()` display the summary of variables.


```{r}

skim(thanksgiving_meals)
  
```

#Think about the task to predict a family income based on their menu: what variables may be useful? Are all of them correct type? 
#Write 2-3 sentences with your explanation.

#There are few variables can be considered. Variables such as, "main_dish" and "stuffing" can be considered as input variables while "family_income" variable is taken as output variable for prediction.
#It is noticed that all variables are string/character type (except "id" variable) and need to convet them as factor variables.


#Think about the task to predict a community type or US_region based on their menu: what variables may be useful? Are all of them correct type?

#"slide10" and "pie9" variables are taken as input variable due to majority of them consumed while "us_region" is considered as output variable. All of the variables are in String/character type and need to convet them as factor variables due to that reason classification method should be used for predication.






#3. Use `fct_reorder` and `parse_number` functions to create a factor variable `family_income`

```{r}
thanksgiving_meals %>%
mutate(family_income = fct_reorder(family_income, parse_number(family_income)))


```


#4. What is the number of people who celebrate?

 
``` {r}

thanksgiving_meals %>%
count(celebrate == "Yes") %>%
kable()

#Should be considered true values

```

#5. What are categories and insights for each main dish served and the method it is prepared?

```{r}

#filter(unique_thanksgiving_meals, main_dish,main_prep)

distinct(thanksgiving_meals, main_dish,main_prep,.keep_all = FALSE)
 

```




#6. Create 3 different data viz showing insights for main dish served and the method. Provide your own legend and use themes.
#Write 2-3 sentences with your explanation of each insight.




#Below bar char displays total consumption of main dish. ggplot and coord_flip () functions are used for bar chart

``` {r}


thanksgiving_meals %>%
 
  ggplot(aes(x = main_dish)) +
geom_bar() +
  coord_flip() +

  labs(y= "Value", x = "Main Dish",colour = "main_dish",
     tiltle = " Distribution of Main Dish", caption = "Figure 1") +
  theme_light()

```


#Below graph shows plot distribution in between Family Income and Main Dish and gglot function is used.

``` {r}

ggplot(data = thanksgiving_meals, aes(x = main_dish, y = family_income)) +
  geom_point()

```

#Below graph displays data distribution of main_dish by using facet_wrap function

```{r}

  thanksgiving_meals %>%
  select(c(family_income,main_dish)) 
ggplot(data = thanksgiving_meals, aes(x = main_dish)) +
geom_bar() +
  coord_flip() +
facet_wrap(~thanksgiving_meals$main_dish) +
  labs(y= "count", y = "main_dish",colour = "main_dish",
     tiltle = " Distribution of main_dish", caption = "Figure 1") +
  theme_light()

```

#7. How many use cranberry sauce? How many use gravy?

``` {r}

thanksgiving_meals %>%
count(cranberry == "Homemade" | cranberry == "Canned" | cranberry == "Other (please specify)") %>%
kable()

thanksgiving_meals %>%
count(gravy == "Yes") %>%
  kable()

```

#8-9. What is the distribution of those who celebrate across income ranges. Create a data viz.
#Write 2-3 sentences with your explanation of each insight.

#Below barchart displays all celebration as per thier  level of family_income.Family Income variable use for y axis and data is filtered by using celebrate = "Yes" and they displayed in the bar by using geom_bar function.

```{r}

ggplot(thanksgiving_meals, aes(y=family_income)) + 
  geom_bar(celebrate = "Yes") 


```





#10. Use the following code to create a new data set

``` {r}

new_dataset  <- thanksgiving_meals %>%
  
select(id, starts_with("side"),
         starts_with("pie"),
         starts_with("dessert")) %>%
  select(-side15, -pie13, -dessert12) %>%
  gather(type, value, -id) %>%
  filter(!is.na(value),
         !value %in% c("None", "Other (please specify)")) %>%
  mutate(type = str_remove(type, "\\d+"))
  
```


  
#Write 2-3 sentences with your explanation of what it does.
  
#In above code, First I create data set called "new_dataset" and assigned original data set. Then it selects the data starts with "side", pie" and "dessert". Then select "side15", "pie13", "dessert12" columns.
#Thereafter, it gathers columns of "side","pie" and "desert" to "type". Then "side","pie" and "desert" vallues are filled into "value". Then filter "N/A" and return "false" values. Then it filter and remove values of "None", "Other (please specify)" from the selected coulumns. Then mutate the type.





#11-12. Intall package `widyr` and use `pairwise_cor()` function https://www.rdocumentation.org/packages/widyr/versions/0.1.3/topics/pairwise_cor
#Write 2-3 sentences with your explanation of what it does.

#"pairwise_cor" function searches correlations of items pairs in a column, according to a "feature" column that connects them together. It cmes under "widyr" package. According to the data set it shows the how corerelate item1 and item2 with corerelation value.
 

#Use this code for the new dataset
#pairwise_cor(value, id, sort = TRUE)


``` {r}


new_dataset  %>%
pairwise_cor(value, id, sort = TRUE)

```


#13. Use `lm()` or randomForest() function to build a model that predict a family income based on data in the dataset.


#Compare 3 models using different set of input variables. Use different number of variables.






<!--new_dataset2  <- thanksgiving_meals %>%
  
select(id,main_dish,main_prep, 
        
         family_income) %>%

  gather(main_dish, main_prep,-family_income, -id) %>%
 filter(!is.na(main_prep),
         main_prep %in% c("Chicken", "Turkey")) %>%
 filter(!is.na(family_income),
         !family_income %in% c("None", "Other (please specify)","Prefer not to answer")) -->

  





<!--

new_dataset3  <- thanksgiving_mealsV2 %>%
  
select(main_dish,main_prep, 
        
         family_income,pie9) %>%

  gather(main_dish, main_prep,-family_income,-pie9) %>%
 filter(!is.na(main_prep),
         main_prep %in% c("Chicken", "Turkey")) %>%
 filter(!is.na(family_income),
         !family_income %in% c("None", "Other (please specify)","Prefer not to answer"))%>%
   filter(!is.na(pie9),
         !pie9 %in% c("N/A"))%>%
  mutate(family_income = str_remove(family_income, "\\d+"))   -->


  





``` {r}

thanksgiving_mealsV2 <- thanksgiving_meals

thanksgiving_mealsV2 
thanksgiving_mealsV2$family_income = as.factor(thanksgiving_mealsV2$family_income)

factor(thanksgiving_mealsV2$family_income)
str(thanksgiving_mealsV2)

class(thanksgiving_mealsV2)

```

``` {r}

new_dataset3  <- thanksgiving_mealsV2 %>%
  
  select(family_income,main_dish,stuffing,main_prep) %>%
  
  gather(main_dish,main_prep,-main_prep,-main_dish,-family_income,-stuffing) %>%
  filter(!is.na(stuffing),
         !stuffing %in% c("N/A","None", "Other (please specify)")) %>%
  filter(!is.na(family_income),
         !family_income %in% c("None", "Other (please specify)","Prefer not to answer"))%>%
  filter(!is.na(main_prep),
         !main_prep %in% c("N/A","Other (please specify)"))%>%
    filter(!is.na(main_dish),
         !main_dish %in% c("Other (please specify)"))%>%
      filter(!is.na(main_dish),
         !main_dish %in% c("NA"))%>%
  mutate(family_income = str_remove(family_income, "\\d+"))


new_datasetv2 <- new_dataset3 
new_datasetv2$family_income <- as.factor(new_datasetv2$family_income)

class(new_datasetv2$main_dish)

str(new_dataset3)

```

``` {r}

model1 <- randomForest(family_income ~ main_prep+ stuffing, data = new_datasetv2, na.action = na.omit)
print(model1)

model2 <- randomForest(family_income ~ main_prep + main_dish +stuffing, data = new_datasetv2, na.action = na.omit)
print(model2)

model3 <- randomForest(family_income ~ main_dish + stuffing, data = new_datasetv2, na.action = na.omit)
print(model3)

```

#Explain your choice of variables (

#Write 2 sentences explaining which model os best.

#"family_income" variable is selected as output variable while "main_dish", "main_prep" and "stuffing" variables are selected as input variables because it contains required data for modeling. Since "family_income output variable is non numeric, I selected "Classification" model and used "randomForest" function in order to conduct modeling. According to the results of below models, the most accrate model is model3 due to less error rate.


<!--# Classification starts



#Classification Model 1


model1 <- randomForest(family_income ~ main_prep, data = new_dataset3, na.action = na.omit)
print(model1)

#Classification Model 2

model2 <- randomForest(family_income ~ main_prep + pie9, data = new_dataset2, na.action = na.omit)
print(model2)

#Classification Model 3

model3 <- randomForest(family_income ~ side9 + pie9 , data = new_dataset2, na.action = na.omit)
print(model3)

-->



































